Background for transient faults in asynchronous circuits

### 2019-04-07 draft_together3.tex
hereafter delete valid initial state from lemma defs

The internal wires in the logic blocks that are not included in the state graphs need to have values that are semi-modularity consistent for the circuit to proceed with no glitches.  The internal wires exist in the logic blocks in the original circuit and thus exist in the fault tolerant circuit from the circuit transformation.  The actual values of these wires do not matter if the inputs to the logic blocks follow the semi-modularity property, and if the internal wires are initialized properly.  This arises from the original synthesis method to synthesize the circuit from an underlying state graph.  
Additionally, it does not suffice for the inputs to the logic blocks to be from a valid trace of the state graph; the timing matters as well.  The semi-modularity property must be preserved:  if the logic block output is excited then it must remain excited until a transition on its output occurs.  Since certain inputs which are valid states and arise from valid transitions may cause the logic block to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.  %maybe needs an example
Thus to satisfy semi-modularity, the inputs wait at certain input states until the output transitions.  Then the internal wires of the logic block are termed {\em semi-modularity consistent} if the following property is true:  if the inputs follow semi-modularity then there are no glitches at the output and that once the output is excited it remains excited until it transitions. \\%newly added

@@

\begin{lemma}[1]
If the A half of the fault tolerant circuit starts in a valid initial state, and where $\sigma$ is the trace of the fault tolerant circuit, then $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.  The trace $\sigma$ can be finite or infinite in length.  
%Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault tolerant circuit (the trace is possibly finite).  
By symmetry this is also true for the B half if we exchange A and B in the statement above.

@@

\begin{figure}
  \centering
    \includegraphics{flowl2c3}
  \caption{The wires in each row are in order of logic block, C1, C2, C3, W.  Each row represents half of the duplicated circuit, ie. top row are A half wires and bottom row are B half wires.  'Un' denotes that the logic block is unexcited and 'Exc' denotes the logic block is excited.  Blue arrows indicate a case change caused by transitions elsewhere in the circuit.  Black arrows indicate a wire transition.}
  \label{fig:l21}
\end{figure}
%fixed 
\begin{lemma}[2.1]
For any state in a trace $\sigma$ of the fault tolerant circuit starting in a valid initial state, all wire blocks are in one of the cases in figure \ref{fig:l21}.
\end{lemma}
\begin{proof}
We show by induction that for the fault tolerant circuit, each wire block will be in one of the cases in the above figure.  The figure halves the number of cases, case 11 is the inversion of case 1 (with the 0's and 1's inverted) and from case 11 the state transition goes through the second half of the cases in figure \ref{fig:l21} but inverted.  Thus we only need to analyze up to case 10.  Because both halves satisfy the conditions of Lemma 1, those properties can be applied directly.\\

>>>>

The internal wires in the logic blocks which are not included in the state graphs need to have values that are semi-modularity consistent for the circuit to proceed with no glitches.  The internal wires exist in the logic blocks in the original circuit and thus exist in the fault tolerant circuit from the circuit transformation.  The actual values of these wires do not matter if the inputs to the logic blocks follow the semi-modularity property, and if the internal wires are initialized properly.  This arises from the original synthesis method to synthesize the circuit from an underlying state graph.  
Additionally, it does not suffice for the inputs to the logic blocks to be from a valid trace of the state graph; the timing matters as well.  The semi-modularity property must be preserved:  if the logic block output is excited then it must remain excited until a transition on its output occurs.  Since certain inputs which are valid states and arise from valid transitions may cause the logic block to become unexcited before a transition occurs and thus break the semi-modularity property, we require this more stringent criteria.  %maybe needs an example
Thus to satisfy semi-modularity, the inputs wait at certain input states until the output transitions.  Then the internal wires of the logic block are termed {\em semi-modularity consistent} if the following properties are true:  if the inputs follow semi-modularity then there are no glitches at the output; and once the output is excited it remains excited until the output transitions. \\%newly added

@@

\begin{lemma}[1]
If the A half of the fault tolerant circuit starts in a valid initial state, and where $\sigma$ is the trace of the fault tolerant circuit, then:
\begin{itemize}
\item  $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
\item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
\item For all states $s$ in $\sigma$, $h^A(s)$ being excited corresponds to exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.  And $h^A(s)$ being unexcited corresponds to none of the four conditions are true.
\end{itemize}

The trace $\sigma$ can be finite or infinite in length.  
%Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault tolerant circuit (the trace is possibly finite).  
By symmetry this is also true for the B half if we exchange A and B in the statement above.

@@

\begin{figure}
  \centering
    \includegraphics{flowl2c3}
  \caption{The wires in each row are in order of logic block, C1, C2, C3, W.  Each row represents half of the duplicated circuit, ie. top row are A half wires and bottom row are B half wires.  'Un' denotes that the logic block is unexcited and 'Exc' denotes the logic block is excited.  Blue arrows indicate a case change caused by transitions elsewhere in the circuit.  Black arrows indicate a wire transition.}
  \label{fig:l21}
\end{figure}
%fixed 
\begin{lemma}[2.1]
For any state in a trace of the fault tolerant circuit starting in a valid initial state, all wire blocks are in one of the cases in figure \ref{fig:l21}.
\end{lemma}
\begin{proof}
We show by induction that for the fault tolerant circuit, each wire block will be in one of the cases in the above figure.  The figure halves the number of cases, case 11 is the inversion of case 1 (with the 0's and 1's inverted) and from case 11 the state transition goes through the second half of the cases in figure \ref{fig:l21} but inverted.  Thus we only need to analyze up to case 10.  Because both halves satisfy the conditions of Lemma 1, those properties can be applied directly.\\
